%! TEX program = lualatex

%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}
% Set applicant's personal data for header
% Full name
\name{Jihoon Og}
% This is my contact information and location 
\contacts{(403) 393-7144 \linebreak jihoonog@gmail.com \linebreak Edmonton, AB}

\begin{document}

% Print the header
\makeheader

% Print Research interests
% \begin{cvsection}{Research Interests}
%   \begin{center}
%     ~\\
%     \begin{itemize*}
%       \item Operating Systems
%       \item Performance modeling
%       \item Heterogenous Computing
%     \end{itemize*}
%   \end{center}
% \end{cvsection}
% \vspace*{-12pt}

% Print Education
\begin{cvsection}{Education}
  \begin{cvsubsection}{Edmonton, AB}{University of Alberta}{Fall 2018 -- December 2021 (Expected)}
    \begin{itemize}
      \item B.Sc. Honors in Computing Science -- GPA: 3.4.
      \item \textbf{Undergraduate Coursework:} 
        Operating System Concepts,
        File and Database Systems,
        Computer Systems and Architecture II,
        Calculus II,
        Image Recognition,
        Software Process and Product Management,
        GPU Programming, 
        Software Defined Radio, 
        Web Application and Architecture.
      \item \textbf{Dean's Honor Roll:} For the 2018-2019 academic year. 
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{Lethbridge, AB}{University of Lethbridge}{Fall 2016 -- Spring 2018}
    \begin{itemize}   
      \item B.Sc. in Computer Science with a minor in Economics - GPA: 3.96.
      \item \textbf{Undergraduate Coursework:} 
        Fundamentals of Programming,
        Discrete Mathematics,
        Digital Systems,
        Linear Algebra I,
        Computer Architecture,
        Data Structure and Algorithms,
        Artificial Intelligence,
        Music Software Design,
        Statistics I,
        Practical Software Development.
      \item \textbf{Dean's Honor Roll:} For the 2016 - 2017 and 2017 - 2018 academic years.
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}

% Print Teaching Experience
\vspace*{-10pt}
\begin{cvsection}{Teaching Experience}
  \begin{cvsubsection}{Undergraduate Teaching Assistant}{University of Alberta}{January 2021 -- April 2021}	
    \vspace*{8pt}
    \begin{itemize}
      \item Created weekly weekly assignments for Introduction to Tangible Computing 2 
      \item Attended lab sessions to help students with course content
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{Undergraduate Teaching Assistant}{University of Alberta}{September 2020 -- December 2020}	
    \vspace*{8pt}
    \begin{itemize}
      \item Created worksheets for Introduction to Tangible Computing 1 
      \item Created mid-term materials for the algorithms and data structures specifically on Huffman trees and coding 
      \item Attended lab sessions to help students with course content
    \end{itemize}
  \end{cvsubsection}
  
  \begin{cvsubsection}{Undergraduate Teaching Assistant}{University of Alberta}{September 2019 -- December 2019}	
    \vspace*{8pt}
    \begin{itemize}
      \item Created assignments for Operating Systems Concepts. 
      \item Attended lab sessions to help students with course content.
    \end{itemize}
  \end{cvsubsection}
  
\end{cvsection}

% Print Work Experience
\vspace*{-10pt}
\begin{cvsection}{Work Experience}
   \begin{cvsubsection}{Assistant Engineer, Intern}{Huawei Canada}{May 2020 -- August 2021}
    % \vspace*{8pt}
    \begin{itemize}
      \item Created an automated testing and performance analysis infrastructure to help developers improve compiler performance.
      \item Performed profiling analysis on AI specific algorithms and improve upon them.
      \item Performed performance analysis on the benefit of Out-of-Order Commit using gem5 and LLVM to show hardware and software benefits.
      \item Developed an ML-guided performance prediction model for LLVM IR.
    \end{itemize}
  \end{cvsubsection}
  
  \begin{cvsubsection}{Research Assistant, Summer Student}{University of Alberta}{May 2019 -- August 2019}
    \vspace*{8pt}		
    \begin{itemize}
      \item Developed a real-time occupancy flow and recognition algorithm for a low resolution infrared camera.
      \item Established 2 Linux servers for machine learning, and algorithmic testing for the university's sustainable computing and networking lab.
    \end{itemize}
  \end{cvsubsection}
 
  \begin{cvsubsection}{Research Assistant, Summer Student}{University of Lethbridge}{May 2018 -- August 2018}	
    \vspace*{8pt}
    \begin{itemize}
      \item Developed an API written in C++ for a neuromorphic camera using software development techniques to streamline algorithm development and testing.
      \item Created a comprehensive dataset using the neuromorphic camera to be used by researchers for algorithmic testing and evaluation.
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}

% Print Independent Studies
\vspace*{-10pt}
\begin{cvsection}{Independent Studies}
  \begin{cvsubsection}{Undergraduate Student}{University of Alberta}{September 2019 -- January 2020}
    % \vspace*{5pt}
    \begin{itemize}
      \item Explored Software Defined Radio using GNU Radio on the ADALM-PLUTO platform.
      \item Researched real time storage and processing of multiple radio bands on the Ettus X310 SDR platform.
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}

% Print Conferences
\vspace*{-10pt}
\begin{cvsection}{Conferences}
  \begin{cvsubsection}{Canadian Undergraduate Computer Science Conference}{University of Calgary}{2018}
  \end{cvsubsection}
\end{cvsection}

% Print Skills
\vspace*{-10pt}
\begin{cvsection}{Skills}
  \begin{cvsubsection}{Programming Languages}{}{}	
    \begin{itemize}
      \item \emph{(Proficient):} C/C++, Python, Bash, R  
      \item \emph{(Familiar):} Java, JavaScript, SQL, Scheme, SQLite, Arduino
    \end{itemize}
  \end{cvsubsection}
  \begin{cvsubsection}{Frameworks and Libraries}{}{}
    \begin{itemize}
      \item \emph{(Proficient):} Django, Gem5, Pytorch, OpenCV, LLVM
      \item \emph{(Familiar):)} ROS, Tensorflow
    \end{itemize}
  \end{cvsubsection}
  \begin{cvsubsection}{Tools}{}{}
    \begin{itemize}
      \item \emph{(Proficient):} GDB, Valgrind, Git 
      \item \emph{(Familiar):} gprof, gcov
    \end{itemize}
  \end{cvsubsection}
  \begin{cvsubsection}{Others}{}{}
    \begin{itemize}
    \item \emph{(Proficient):} Linux, Microsoft Office Suite (Word, Excel)
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}

\vspace*{-10pt}
\begin{cvsection}{Projects}
  \begin{cvsubsection}{CMPUT-404 Software Project}{}{2021}
    \vspace*{8pt}
    \begin{itemize}
      \item Helped develope a peer-to-peer blogging and social networking platform for CMPUT 404 Web Applications and Architecture.
      \item Allow users to see and connect to other users on a different server. 
      \item Developed using Django for the back-end and React for the front-end. 
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{CMPUT-401 Software Project}{}{2020}
    \vspace*{8pt}
    \begin{itemize}
      \item Helped develope an election generation system for the University of Alberta Students' Union
      \item Developed using Django for the back-end and Vue for the front-end.
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}

% Print awards and scholarships
\vspace*{-10pt}
\begin{cvsection}{Awards and Scholarships}
  \begin{cvsubsection}{}{}{}
    \begin{itemize}
      \item \textbf{2020/2021:} Jason Lang Scholarship
      \item \textbf{2019/2020:} Jason Lang Scholarship
      \item \textbf{2018/2019:} Jason Lang Scholarship
      \item \textbf{2017/2018:} Louise McKinney Post-secondary Scholarship 
      \item \textbf{2018:} NSERC Undergraduate Student Research Awards
      \item \textbf{2016:} Alexander Rutherford Scholarship
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}
\newpage
% Print Languages
\vspace*{-10pt}
\begin{cvsection}{Languages}
  \begin{cvsubsection}{}{}{}	
    \begin{itemize}
      \item \emph{(Native)} English  
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}
% Print Extracurricular and other stuff
\vspace*{-10pt}
\begin{cvsection}{Leadership and Extracurriculars}{}{}
  \begin{cvsubsection}{Senior Representative}{UACS (University of Alberta)}{2019 -- 2020}
    \vspace*{5pt}
    \begin{itemize}
      \item Represented the senior student body of Computing Science students through the \textbf{Undergraduate Association of Computing Science (UACS)}
      \item Helped plan events including the Computing Science Graduation Party for newly graduated Computing Science students.
      \item Assisted in the daily operations of UACS, including but not limited to: food restocking, office cleaning, and weekly meetings.        
    \end{itemize}
  \end{cvsubsection}

  \begin{cvsubsection}{Volunteer}{HackED}{2019, 2020}
    \begin{itemize}
      \item Helped setup for the 24-hour event, moving and checking equipments, and helped with registrations.
      \item Assisted teams with debugging code, providing directions to events, and transporting foods and drinks throughout the event.    
    \end{itemize}
  \end{cvsubsection}
  
  \begin{cvsubsection}{Competitor}{Programming Competitions}{2017}
    \begin{itemize}
      \item \textbf{2017 Rocky Mountain Regional ACM ICPC:} Placed 31st out of 52.
      \item \textbf{2017 Alberta Collegiate Programming Contest:} Placed 28th out of 53.
      \item \textbf{2017 Lethbridge Collegiate Programming Contest:} Place 4th in Division 2.
    \end{itemize}
  \end{cvsubsection}
\end{cvsection}




\end{document}
